---
title: "Trial 1B - full data set"
output: html_notebook
---

Load packages:
```{r}
library(pacman)
p_load(psych, haven, tidyverse, GPArotation, multilevel)
```
Import data:
```{r}
surveyfull <- read_spss("../data/The Effect of Various Factors on Childhood Experiences and Adult Perso 3 full.sav")
```
Create STS data frame with full data set:
```{r}
stsfull <- dplyr::select(surveyfull, q0046_0001, q0047_0001, q0048_0001, q0049_0001, q0050_0001, q0051_0001, q0052_0001, q0053_0001, q0054_0001, q0055_0001, q0056_0001, q0057_0001, q0058_0001, q0059_0001, q0060_0001, q0061_0001, q0062_0001, q0063_0001, q0064_0001, q0065_0001, q0066_0001, q0067_0001, q0068_0001, q0069_0001, q0070_0001, q0071_0001, q0072_0001, q0073_0001, q0074_0001, q0075_0001, q0076_0001, q0077_0001, q0078_0001, q0079_0001, q0080_0001, q0081_0001, q0082_0001, q0083_0001, q0084_0001, q0085_0001, q0086_0001, q0087_0001, q0088_0001, q0089_0001, q0090_0001)
```
```{r}
stsfull.dat <- as.data.frame(stsfull)
```
Descriptive stats:
```{r}
describe(stsfull.dat)
```
Trial analysis on survey full:
Using PA
```{r}
parallel.s4 <- fa.parallel(stsfull, fm = 'pa', fa = 'fa')
```
EFA
PAF
5 factors:
```{r}
fivefactor.pa.full <- fa(stsfull,nfactors = 5,rotate = "oblimin",fm="pa")
print(fivefactor.pa.full)
```
Supress factor loadings below 0.49
```{r}
print(fivefactor.pa.full$loadings,cutoff = 0.49)
```
EFA
PAF
4 factors:
```{r}
fourfactor.pa.full <- fa(stsfull,nfactors = 4,rotate = "oblimin",fm="pa")
print(fourfactor.pa.full)
```
Supress factor loadings below 0.49
```{r}
print(fourfactor.pa.full$loadings,cutoff = 0.49)
```
EFA
PAF
3 factors:
```{r}
threefactor.pa.full <- fa(stsfull,nfactors = 3,rotate = "oblimin",fm="pa")
print(threefactor.pa.full)
```
Supress factor loadings below 0.49
```{r}
print(threefactor.pa.full$loadings,cutoff = 0.49)
```

Consider psych sep only:
```{r}
stsfull_psych <- dplyr::select(surveyfull, q0059_0001, q0060_0001, q0061_0001, q0062_0001, q0063_0001, q0064_0001, q0065_0001, q0066_0001, q0067_0001, q0068_0001, q0069_0001, q0070_0001, q0071_0001, q0072_0001, q0073_0001, q0074_0001, q0075_0001, q0076_0001, q0077_0001, q0078_0001, q0079_0001, q0080_0001, q0081_0001, q0082_0001, q0083_0001, q0084_0001, q0085_0001, q0086_0001, q0087_0001, q0088_0001, q0089_0001, q0090_0001)

```
Trial analysis on survey full (psych only):
Using PA
```{r}
parallel.s5 <- fa.parallel(stsfull_psych, fm = 'pa', fa = 'fa')
```
EFA
PAF
4 factors
Only psych:
```{r}
fourfactor.pa.full_psych <- fa(stsfull_psych,nfactors = 4,rotate = "oblimin",fm="pa")
print(fourfactor.pa.full_psych)
```
Supress factor loadings below 0.49
```{r}
print(fourfactor.pa.full_psych$loadings,cutoff = 0.49)
```
EFA
PAF
3 factors
Only psych:
```{r}
threefactor.pa.full_psych <- fa(stsfull_psych,nfactors = 3,rotate = "oblimin",fm="pa")
print(threefactor.pa.full_psych)
```
Supress factor loadings below 0.49
```{r}
print(threefactor.pa.full_psych$loadings,cutoff = 0.49)
```
EFA
PAF
2 factors
Only psych:
```{r}
twofactor.pa.full_psych <- fa(stsfull_psych,nfactors = 2,rotate = "oblimin",fm="pa")
print(twofactor.pa.full_psych)
```
Supress factor loadings below 0.49
```{r}
print(twofactor.pa.full_psych$loadings,cutoff = 0.49)
```
Consider phys sep only:
```{r}
stsfull_phys <-dplyr::select(surveyfull, q0046_0001, q0047_0001, q0048_0001, q0049_0001, q0050_0001, q0051_0001, q0052_0001, q0053_0001, q0054_0001, q0055_0001, q0056_0001, q0057_0001, q0058_0001)
```

Trial analysis on survey full (phys only):
Using PA
```{r}
parallel.s6 <- fa.parallel(stsfull_phys, fm = 'pa', fa = 'fa')
```
EFA
PAF
3 factors
Only phys:
```{r}
threefactor.pa.full_phys <- fa(stsfull_phys,nfactors = 3,rotate = "oblimin",fm="pa")
print(threefactor.pa.full_phys)
```
Supress factor loadings below 0.49
```{r}
print(threefactor.pa.full_phys$loadings,cutoff = 0.49)
```
EFA
PAF
2 factors
Only phys:
```{r}
twofactor.pa.full_phys <- fa(stsfull_phys,nfactors = 2,rotate = "oblimin",fm="pa")
print(twofactor.pa.full_phys)
```
Supress factor loadings below 0.49
```{r}
print(twofactor.pa.full_phys$loadings,cutoff = 0.49)
```
EFA
PAF
1 factors
Only phys:
```{r}
onefactor.pa.full_phys <- fa(stsfull_phys,nfactors = 1,rotate = "oblimin",fm="pa")
print(onefactor.pa.full_phys)
```
Supress factor loadings below 0.49
```{r}
print(onefactor.pa.full_phys$loadings,cutoff = 0.49)
```
Alpha on final Phys scale:
```{r}
stsfull_phys_final <-dplyr::select(surveyfull, q0048_0001, q0049_0001, q0050_0001, q0051_0001, q0052_0001, q0053_0001, q0054_0001, q0055_0001, q0056_0001, q0057_0001, q0058_0001)
```
```{r}
alpha_phys_final <- psych::alpha(stsfull_phys_final)
alpha_phys_final
```
Alpha on final Psych scale:
```{r}
stsfull_psych_final <- dplyr::select(surveyfull, q0059_0001, q0060_0001, q0061_0001, q0062_0001, q0064_0001, q0065_0001, q0066_0001, q0067_0001, q0068_0001, q0069_0001, q0070_0001, q0071_0001, q0072_0001, q0074_0001, q0077_0001, q0081_0001, q0082_0001, q0083_0001, q0084_0001, q0085_0001, q0087_0001, q0088_0001, q0089_0001, q0090_0001)
```
```{r}
alpha_psych_final <- psych::alpha(stsfull_psych_final)
alpha_psych_final
```
ITC on final Phys scale:
```{r}
item.total(stsfull_phys_final)
```
ITC on final Psych scale:
```{r}
item.total(stsfull_psych_final)
```
Create full final STS scale (final STS phys + final STS psych)
```{r}
stsfull_final <- cbind(stsfull_phys_final, stsfull_psych_final)
```
create totals:
```{r}
stsfull_final.tot <- stsfull_final
stsfull_phys_final.tot <- stsfull_phys_final
stsfull_psych_final.tot <- stsfull_psych_final
```
```{r}
stsfull_final.tot <- cbind(stsfull_final.tot, total = rowSums(stsfull_final.tot))
stsfull_phys_final.tot <- cbind(stsfull_phys_final.tot, total = rowSums(stsfull_phys_final.tot))
stsfull_psych_final.tot <- cbind(stsfull_psych_final.tot, total = rowSums(stsfull_psych_final.tot))
```
Descriptive stats of scale and subscale totals
```{r}
describe(stsfull_final.tot)
describe(stsfull_phys_final.tot)
describe(stsfull_psych_final.tot)
```
Histograms of full scale and subscale totals:
```{r}
ggplot(data=stsfull_final.tot, aes(stsfull_final.tot$total, fill = "blue")) + 
  geom_histogram()
ggplot(data=stsfull_phys_final.tot, aes(stsfull_phys_final.tot$total, fill = "blue")) + 
  geom_histogram()
ggplot(data=stsfull_psych_final.tot, aes(stsfull_psych_final.tot$total, fill = "blue")) + 
  geom_histogram()
```
Rerun 4 factor psych sep scale on 24 items that loaded:
EFA
PAF
4 factors
Only psych
Items that loaded

Create scale of 24 items that loaded
```{r}
stsfull_psych_loaded <- dplyr::select(surveyfull, q0059_0001, q0060_0001, q0061_0001, q0062_0001, q0064_0001, q0065_0001, q0066_0001, q0067_0001, q0068_0001, q0069_0001, q0070_0001, q0071_0001, q0072_0001, q0074_0001, q0077_0001, q0081_0001, q0082_0001, q0083_0001, q0084_0001, q0085_0001, q0087_0001, q0088_0001, q0089_0001, q0090_0001)
```
Trial analysis on survey (psych only) items that loaded: 
Using PA
```{r}
parallel.s7 <- fa.parallel(stsfull_psych_loaded, fm = 'pa', fa = 'fa')
```
EFA 
PAF 
4 factors 
Only psych
Items that previosly loaded
```{r}
fourfactor.pa.full_psych_loaded <- fa(stsfull_psych_loaded,nfactors = 4,rotate = "oblimin",fm="pa")
print(fourfactor.pa.full_psych_loaded)
```
Supress factor loadings below 0.49
```{r}
print(fourfactor.pa.full_psych_loaded$loadings,cutoff = 0.49)
```
Rerun 3 factor phys sep scale on 11 items that loaded:
EFA
PAF
3 factors
Only phys
Items that previously loaded

Create scale of 11 items that loaded:
```{r}
stsfull_phys_loaded <-dplyr::select(surveyfull, q0048_0001, q0049_0001, q0050_0001, q0051_0001, q0052_0001, q0053_0001, q0054_0001, q0055_0001, q0056_0001, q0057_0001, q0058_0001)
```

Trial analysis on survey full (phys only):
Using PA
```{r}
parallel.s8 <- fa.parallel(stsfull_phys_loaded, fm = 'pa', fa = 'fa')
```
EFA
PAF
3 factors 
Only phys
Items that previously loaded
```{r}
threefactor.pa.full_phys_loaded <- fa(stsfull_phys_loaded,nfactors = 3,rotate = "oblimin",fm="pa")
print(threefactor.pa.full_phys_loaded)
```
Supress factor loadings below 0.49
```{r}
print(threefactor.pa.full_phys_loaded$loadings,cutoff = 0.49)
```
REGRESSIONS

Create data frame for regression (using 35 items in final scale + all BDI items)
```{r}
regression.dat <- dplyr::select(surveyfull, q0048_0001, q0049_0001, q0050_0001, q0051_0001, q0052_0001, q0053_0001, q0054_0001, q0055_0001, q0056_0001, q0057_0001, q0058_0001, q0059_0001, q0060_0001, q0061_0001, q0062_0001, q0064_0001, q0065_0001, q0066_0001, q0067_0001, q0068_0001, q0069_0001, q0070_0001, q0071_0001, q0072_0001, q0074_0001, q0077_0001, q0081_0001, q0082_0001, q0083_0001, q0084_0001, q0085_0001, q0087_0001, q0088_0001, q0089_0001, q0090_0001, q0025_0001, q0026_0001, q0027_0001, q0028_0001, q0029_0001, q0030_0001, q0031_0001, q0032_0001, q0033_0001, q0034_0001, q0035_0001, q0036_0001, q0037_0001, q0038_0001, q0039_0001, q0040_0001, q0041_0001, q0042_0001, q0043_0001, q0044_0001, q0045_0001)
```
Create scale and subscale totals for 
STS full
STS psych
STS phys
BDI
```{r}
regression.dat$stsphys_total <- regression.dat$q0048_0001 + regression.dat$q0049_0001 + regression.dat$q0050_0001 + regression.dat$q0051_0001 + regression.dat$q0052_0001 +  regression.dat$q0053_0001 + regression.dat$q0054_0001 + regression.dat$q0055_0001 + regression.dat$q0056_0001 + regression.dat$q0057_0001 + regression.dat$q0058_0001
```
```{r}
regression.dat$stspsych_total <- regression.dat$q0059_0001 + regression.dat$q0060_0001 + regression.dat$q0061_0001 + regression.dat$q0062_0001 + regression.dat$q0064_0001 + regression.dat$q0065_0001 + regression.dat$q0066_0001 + regression.dat$q0067_0001 + regression.dat$q0068_0001 + regression.dat$q0069_0001 + regression.dat$q0070_0001 + regression.dat$q0071_0001 + regression.dat$q0072_0001 + regression.dat$q0074_0001 + regression.dat$q0077_0001 + regression.dat$q0081_0001 + regression.dat$q0082_0001 + regression.dat$q0083_0001 + regression.dat$q0084_0001 + regression.dat$q0085_0001 + regression.dat$q0087_0001 + regression.dat$q0088_0001 + regression.dat$q0089_0001 + regression.dat$q0090_0001
```
```{r}
regression.dat$stsfull_total <- regression.dat$stsphys_total + regression.dat$stspsych_total
```
```{r}
regression.dat$bdi_total <- regression.dat$q0025_0001 + regression.dat$q0026_0001 + regression.dat$q0027_0001 + regression.dat$q0028_0001 + regression.dat$q0029_0001 + regression.dat$q0030_0001 + regression.dat$q0031_0001 + regression.dat$q0032_0001 + regression.dat$q0033_0001 + regression.dat$q0034_0001 + regression.dat$q0035_0001 + regression.dat$q0036_0001 + regression.dat$q0037_0001 + regression.dat$q0038_0001 + regression.dat$q0039_0001 + regression.dat$q0040_0001 + regression.dat$q0041_0001 + regression.dat$q0042_0001 + regression.dat$q0043_0001 + regression.dat$q0044_0001 + regression.dat$q0045_0001
```
Look at distributions:
```{r}
ggplot(data = regression.dat, mapping = aes(stsphys_total)) +
  geom_histogram(fill = "blue")
ggplot(data = regression.dat, mapping = aes(stspsych_total)) +
  geom_histogram(fill = "blue")
ggplot(data = regression.dat, mapping = aes(stsfull_total)) +
  geom_histogram(fill = "blue")
ggplot(data = regression.dat, mapping = aes(bdi_total)) +
  geom_histogram(fill = "blue")
```
Descriptive stats for 4 variables

Create data frame with 4 variables for regression
```{r}
describe_reg.dat <- dplyr::select(regression.dat, stsphys_total, stspsych_total, stsfull_total, bdi_total)
```
Run descriptive stats:
```{r}
describe(describe_reg.dat)
```
Regression 1:
Phys sep vs depression
```{r}
stsphys_depression.reg <- lm(bdi_total ~ stsphys_total, regression.dat)
summary(stsphys_depression.reg)
```
STS phys does not significantly predict depression. Also the distribution of the scores for the phys sep subscale does not meet the assumption of normal distribution neccessary for a linear regression

Regression 2:
Psych sep vs depression
```{r}
stspsych_depression.reg <- lm(bdi_total ~ stspsych_total, regression.dat)
summary(stspsych_depression.reg)
```
Psych sep is significantly predictive of depression, but with a fairly small effect size (F = 10.42, p = 0.002, r-squared = 0.08)

Regression 3:
Full sep vs depression
```{r}
stsfull_depression.reg <- lm(bdi_total ~ stsfull_total, regression.dat)
summary(stsfull_depression.reg)
```
Full sep is significantly predictive of depression, but with a very small effect size (F = 6.97, p = 0.009, r-squared = 0.05). The drop in effect size between the psych sep subscale and the full sep scale suggests that the psych sep subscale is more useful as a predictive tool on it's own.
-------------------------------------------------
Investigate relationships visually:
```{r}
ggplot(data = regression.dat, mapping = aes(x = stsphys_total, y = bdi_total))+
  geom_point()+
  geom_smooth()
ggplot(data = regression.dat, mapping = aes(x = stspsych_total, y = bdi_total))+
  geom_point()+
  geom_smooth()
ggplot(data = regression.dat, mapping = aes(x = stsfull_total, y = bdi_total))+
  geom_point()+
  geom_smooth()

```
Investigate distributions for scales:
```{r}
ggplot(data = regression.dat, mapping = aes(y = stsphys_total))+
  geom_boxplot()
ggplot(data = regression.dat, mapping = aes(y = stspsych_total))+
  geom_boxplot()
ggplot(data = regression.dat, mapping = aes(y = stsfull_total))+
  geom_boxplot()
ggplot(data = regression.dat, mapping = aes(y = bdi_total))+
  geom_boxplot()
```











