---
title: "Trial 1B - full data set"
output: html_notebook
---

Load packages:
```{r}
library(pacman)
p_load(psych, haven, tidyverse, GPArotation, multilevel)
```
Import data:
```{r}
surveyfull <- read_spss("../thesis_trial1/data/The Effect of Various Factors on Childhood Experiences and Adult Perso 3 full.sav")
```
Create STS data frame with full data set:
```{r}
stsfull <- select(surveyfull, q0046_0001, q0047_0001, q0048_0001, q0049_0001, q0050_0001, q0051_0001, q0052_0001, q0053_0001, q0054_0001, q0055_0001, q0056_0001, q0057_0001, q0058_0001, q0059_0001, q0060_0001, q0061_0001, q0062_0001, q0063_0001, q0064_0001, q0065_0001, q0066_0001, q0067_0001, q0068_0001, q0069_0001, q0070_0001, q0071_0001, q0072_0001, q0073_0001, q0074_0001, q0075_0001, q0076_0001, q0077_0001, q0078_0001, q0079_0001, q0080_0001, q0081_0001, q0082_0001, q0083_0001, q0084_0001, q0085_0001, q0086_0001, q0087_0001, q0088_0001, q0089_0001, q0090_0001)
```
```{r}
stsfull.dat <- as.data.frame(stsfull)
```
Descriptive stats:
```{r}
describe(stsfull.dat)
```
Trial analysis on survey full:
Using PA
```{r}
parallel.s4 <- fa.parallel(stsfull, fm = 'pa', fa = 'fa')
```
EFA
PAF
5 factors:
```{r}
fivefactor.pa.full <- fa(stsfull,nfactors = 5,rotate = "oblimin",fm="pa")
print(fivefactor.pa.full)
```
Supress factor loadings below 0.49
```{r}
print(fivefactor.pa.full$loadings,cutoff = 0.49)
```
EFA
PAF
4 factors:
```{r}
fourfactor.pa.full <- fa(stsfull,nfactors = 4,rotate = "oblimin",fm="pa")
print(fourfactor.pa.full)
```
Supress factor loadings below 0.49
```{r}
print(fourfactor.pa.full$loadings,cutoff = 0.49)
```
EFA
PAF
3 factors:
```{r}
threefactor.pa.full <- fa(stsfull,nfactors = 3,rotate = "oblimin",fm="pa")
print(threefactor.pa.full)
```
Supress factor loadings below 0.49
```{r}
print(threefactor.pa.full$loadings,cutoff = 0.49)
```

Consider psych sep only:
```{r}
stsfull_psych <- select(surveyfull, q0059_0001, q0060_0001, q0061_0001, q0062_0001, q0063_0001, q0064_0001, q0065_0001, q0066_0001, q0067_0001, q0068_0001, q0069_0001, q0070_0001, q0071_0001, q0072_0001, q0073_0001, q0074_0001, q0075_0001, q0076_0001, q0077_0001, q0078_0001, q0079_0001, q0080_0001, q0081_0001, q0082_0001, q0083_0001, q0084_0001, q0085_0001, q0086_0001, q0087_0001, q0088_0001, q0089_0001, q0090_0001)

```
Trial analysis on survey full (psych only):
Using PA
```{r}
parallel.s5 <- fa.parallel(stsfull_psych, fm = 'pa', fa = 'fa')
```
EFA
PAF
4 factors
Only psych:
```{r}
fourfactor.pa.full_psych <- fa(stsfull_psych,nfactors = 4,rotate = "oblimin",fm="pa")
print(fourfactor.pa.full_psych)
```
Supress factor loadings below 0.49
```{r}
print(fourfactor.pa.full_psych$loadings,cutoff = 0.49)
```
EFA
PAF
3 factors
Only psych:
```{r}
threefactor.pa.full_psych <- fa(stsfull_psych,nfactors = 3,rotate = "oblimin",fm="pa")
print(threefactor.pa.full_psych)
```
Supress factor loadings below 0.49
```{r}
print(threefactor.pa.full_psych$loadings,cutoff = 0.49)
```
EFA
PAF
2 factors
Only psych:
```{r}
twofactor.pa.full_psych <- fa(stsfull_psych,nfactors = 2,rotate = "oblimin",fm="pa")
print(twofactor.pa.full_psych)
```
Supress factor loadings below 0.49
```{r}
print(twofactor.pa.full_psych$loadings,cutoff = 0.49)
```
Consider phys sep only:
```{r}
stsfull_phys <-select(surveyfull, q0046_0001, q0047_0001, q0048_0001, q0049_0001, q0050_0001, q0051_0001, q0052_0001, q0053_0001, q0054_0001, q0055_0001, q0056_0001, q0057_0001, q0058_0001)
```

Trial analysis on survey full (phys only):
Using PA
```{r}
parallel.s6 <- fa.parallel(stsfull_phys, fm = 'pa', fa = 'fa')
```
EFA
PAF
3 factors
Only phys:
```{r}
threefactor.pa.full_phys <- fa(stsfull_phys,nfactors = 3,rotate = "oblimin",fm="pa")
print(threefactor.pa.full_phys)
```
Supress factor loadings below 0.49
```{r}
print(threefactor.pa.full_phys$loadings,cutoff = 0.49)
```
EFA
PAF
2 factors
Only phys:
```{r}
twofactor.pa.full_phys <- fa(stsfull_phys,nfactors = 2,rotate = "oblimin",fm="pa")
print(twofactor.pa.full_phys)
```
Supress factor loadings below 0.49
```{r}
print(twofactor.pa.full_phys$loadings,cutoff = 0.49)
```
EFA
PAF
1 factors
Only phys:
```{r}
onefactor.pa.full_phys <- fa(stsfull_phys,nfactors = 1,rotate = "oblimin",fm="pa")
print(onefactor.pa.full_phys)
```
Supress factor loadings below 0.49
```{r}
print(onefactor.pa.full_phys$loadings,cutoff = 0.49)
```
Alpha on final Phys scale:
```{r}
stsfull_phys_final <-select(surveyfull, q0048_0001, q0049_0001, q0050_0001, q0051_0001, q0052_0001, q0053_0001, q0054_0001, q0055_0001, q0056_0001, q0057_0001, q0058_0001)
```
```{r}
alpha_phys_final <- psych::alpha(stsfull_phys_final)
alpha_phys_final
```
Alpha on final Psych scale:
```{r}
stsfull_psych_final <- select(surveyfull, q0059_0001, q0060_0001, q0061_0001, q0062_0001, q0064_0001, q0065_0001, q0066_0001, q0067_0001, q0068_0001, q0069_0001, q0070_0001, q0071_0001, q0072_0001, q0074_0001, q0077_0001, q0081_0001, q0082_0001, q0083_0001, q0084_0001, q0085_0001, q0087_0001, q0088_0001, q0089_0001, q0090_0001)
```
```{r}
alpha_psych_final <- psych::alpha(stsfull_psych_final)
alpha_psych_final
```
ITC on final Phys scale:
```{r}
item.total(stsfull_phys_final)
```
ITC on final Psych scale:
```{r}
item.total(stsfull_psych_final)
```
Create full final STS scale (final STS phys + final STS psych)
```{r}
stsfull_final <- cbind(stsfull_phys_final, stsfull_psych_final)
```
create totals:
```{r}
stsfull_final.tot <- stsfull_final
stsfull_phys_final.tot <- stsfull_phys_final
stsfull_psych_final.tot <- stsfull_psych_final
```
```{r}
stsfull_final.tot <- cbind(stsfull_final.tot, total = rowSums(stsfull_final.tot))
stsfull_phys_final.tot <- cbind(stsfull_phys_final.tot, total = rowSums(stsfull_phys_final.tot))
stsfull_psych_final.tot <- cbind(stsfull_psych_final.tot, total = rowSums(stsfull_psych_final.tot))
```
Descriptive stats of scale and subscale totals
```{r}
describe(stsfull_final.tot)
describe(stsfull_phys_final.tot)
describe(stsfull_psych_final.tot)
```
Histograms of full scale and subscale totals:
```{r}
ggplot(data=stsfull_final.tot, aes(stsfull_final.tot$total, fill = "blue")) + 
  geom_histogram()
ggplot(data=stsfull_phys_final.tot, aes(stsfull_phys_final.tot$total, fill = "blue")) + 
  geom_histogram()
ggplot(data=stsfull_psych_final.tot, aes(stsfull_psych_final.tot$total, fill = "blue")) + 
  geom_histogram()
```











