---
title: "Trial 1A - partial data set"
output: html_notebook
---

Load packages:
```{r}
library(pacman)
p_load(psych, haven, tidyverse, GPArotation)
```
Import data:
```{r}
survey1 <- read_spss("../thesis_trial1/data/The Effect of Various Factors on Childhood Experiences and Adult Perso.sav")
survey2 <- read_spss("../thesis_trial1/data/The Effect of Various Factors on Childhood Experiences and Adult Perso 2.sav")
```

Create STS data frame with partial data set:
```{r}
sts <- select(survey2, q0046_0001, q0047_0001, q0048_0001, q0049_0001, q0050_0001, q0051_0001, q0052_0001, q0053_0001, q0054_0001, q0055_0001, q0056_0001, q0057_0001, q0058_0001, q0059_0001, q0060_0001, q0061_0001, q0062_0001, q0063_0001, q0064_0001, q0065_0001, q0066_0001, q0067_0001, q0068_0001, q0069_0001, q0070_0001, q0071_0001, q0072_0001, q0073_0001, q0074_0001, q0075_0001, q0076_0001, q0077_0001, q0078_0001, q0079_0001, q0080_0001, q0081_0001, q0082_0001, q0083_0001, q0084_0001, q0085_0001, q0086_0001, q0087_0001, q0088_0001, q0089_0001, q0090_0001)
```

Trial analysis on survey2:
Using OLS
```{r}
parallel.s1 <- fa.parallel(sts, fm = 'minres', fa = 'fa')
```
Trial analysis on survey2:
Using ML
```{r}
parallel.s2 <- fa.parallel(sts, fm = 'ml', fa = 'fa')
```
EFA
OLS
5 factors:
```{r}
fivefactor.ols <- fa(sts,nfactors = 5,rotate = "oblimin",fm="minres")
print(fivefactor.ols)
```
Supress factor loadings below 0.49
```{r}
print(fivefactor.ols$loadings,cutoff = 0.49)
```
EFA
ML
5 factors:
```{r}
fivefactor.ml <- fa(sts,nfactors = 5,rotate = "oblimin",fm="ml")
print(fivefactor.ml)
```
Supress factor loadings below 0.49
```{r}
print(fivefactor.ml$loadings,cutoff = 0.49)
```
EFA
OLS
7 factors:
```{r}
sevenfactor.ols <- fa(sts,nfactors = 7,rotate = "oblimin",fm="minres")
print(sevenfactor.ols)
```
Supress factor loadings below 0.49
```{r}
print(sevenfactor.ols$loadings,cutoff = 0.49)
```
Trial analysis on survey2:
Using PA
```{r}
parallel.s3 <- fa.parallel(sts, fm = 'pa', fa = 'fa')
```
EFA
PAF
7 factors:
```{r}
sevenfactor.pa <- fa(sts,nfactors = 7,rotate = "oblimin",fm="pa")
print(sevenfactor.pa)
```
Supress factor loadings below 0.49
```{r}
print(sevenfactor.pa$loadings,cutoff = 0.49)
```
EFA
PAF
5 factors:
```{r}
fivefactor.pa <- fa(sts,nfactors = 5,rotate = "oblimin",fm="pa")
print(fivefactor.pa)
```
Supress factor loadings below 0.49
```{r}
print(fivefactor.pa$loadings,cutoff = 0.49)
```
EFA
PAF
4 factors:
```{r}
fourfactor.pa <- fa(sts,nfactors = 4,rotate = "oblimin",fm="pa")
print(fourfactor.pa)
```
Supress factor loadings below 0.49
```{r}
print(fourfactor.pa$loadings,cutoff = 0.49)
```
EFA
PAF
3 factors:
```{r}
threefactor.pa <- fa(sts,nfactors = 3,rotate = "oblimin",fm="pa")
print(threefactor.pa)
```
Supress factor loadings below 0.49
```{r}
print(threefactor.pa$loadings,cutoff = 0.49)
```
EFA
PAF
4 factors:
Varimax rotation
```{r}
fourfactor.pa.orth <- fa(sts,nfactors = 4,rotate = "varimax",fm="pa")
print(fourfactor.pa.orth)
```
Supress factor loadings below 0.49
```{r}
print(fourfactor.pa.orth$loadings,cutoff = 0.49)
```














